The Weakly Nonlinear Magnetorotational Instability in a Global, Cylindrical Taylor-Couette Flow

### 2016-10-04 paper/widegap_mri_paper.tex
edited saturation mechanism text to reflect our findings in paper I

Because it is governed by a real GLE, the saturated standard MRI state may be unstable to the Eckhaus instability, in which the wavelength of the large-scale pattern is adjusted \citep[e.g.][]{Hoyle:2006}. Preliminary investigation of the GLE behavior for the standard MRI coefficients derived here indicates that when the simulated vertical domain is large (i.e. spans multiple critical wavelengths), the amplitude function is modulated in $Z$, but always be bounded by $\alpha_{s} = \pm \sqrt{b/c}$, as must be the case for the one-dimensional real GLE. In Figure \ref{fig:smri_streamfuncs} we plot the saturated state perturbation structure of the fiducial standard MRI, up to and including second order disturbances. We use a constant saturation amplitude, but note that a nonconstant $\alpha_{s}$ would introduce more vertical structure. We similarly plot the total stress, i.e. the sum of the Reynolds and Maxwell stresses in our domain (Figure \ref{fig:total_stress}). We find that the saturation mechanism for weakly nonlinear TC flow is a reduction in the background shear profile. Thus the bounded cylindrical geometry considered here saturates via the same mechanism as in the narrow gap limit (\citei{Umurhan:2007hs}).

>>>>

Because it is governed by a real GLE, the saturated standard MRI state may be unstable to the Eckhaus instability, in which the wavelength of the large-scale pattern is adjusted \citep[e.g.][]{Hoyle:2006}. Preliminary investigation of the GLE behavior for the standard MRI coefficients derived here indicates that when the simulated vertical domain is large (i.e. spans multiple critical wavelengths), the amplitude function is modulated in $Z$, but always be bounded by $\alpha_{s} = \pm \sqrt{b/c}$, as must be the case for the one-dimensional real GLE. In Figure \ref{fig:smri_streamfuncs} we plot the saturated state perturbation structure of the fiducial standard MRI, up to and including second order disturbances. We use a constant saturation amplitude, but note that a nonconstant $\alpha_{s}$ would introduce more vertical structure. We similarly plot the total stress, i.e. the sum of the Reynolds and Maxwell stresses in our domain (Figure \ref{fig:total_stress}). As in Paper I, we find that the saturation mechanism for weakly nonlinear TC flow is a combination of reduced shear and redistributed and amplified background $B_z$. This strongly suggests that the underlying physics remains the same in the wide gap geometry, despite the addition of curvature terms.
